{\itshape Advanced Robotics} A simple path optimization method for motion planning

### 2015-10-21 paper.tex
Add missing results, commit table, modify figures

% The following packages can be found on http:\\www.ctan.org
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{color}
\usepackage{graphicx} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{mathrsfs}
\DeclareMathOperator*{\argmin}{argmin}
\usepackage{algorithm}
\usepackage{algpseudocode}  %\usepackage[noend]{algpseudocode}
\algtext*{EndWhile}% Remove "end while" text
\algtext*{EndIf}% Remove "end if" text
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{proof}
\newtheorem{property}{Property}
\usepackage[numbers]{natbib}
\algnewcommand\algorithmicinput{\textbf{input:}}
\algnewcommand\INPUT{\item[\algorithmicinput]}
\algnewcommand\algorithmicoutput{\textbf{output:}}
\algnewcommand\OUTPUT{\item[\algorithmicoutput]}
\makeatletter
%\let\NAT@parse\undefined % allow hyperref to work with ieeeconf.cls for bib numbers
\makeatother
\usepackage{hyperref}
%\usepackage{cite}

@@

\jvol{00} \jnum{00} \jyear{2015} \jmonth{October}

@@

\author{Myl\`{e}ne Campana$^{a,b}$ $^{\ast}$ \thanks{$^\ast$Corresponding author. Email: mcampana@laas.fr}, Florent Lamiraux$^{a,b}$ and Jean-Paul Laumond$^{a,b}$
\\\vspace{6pt}
$^{a}${\em{LAAS-CNRS, Toulouse, France}};
$^{b}${\em{ This work has been supported by the project ERC Advanced Grant 340050 Actanthrope and by the FP~7 project Factory in a Day under grant agreement n°~609206 }}
}
\maketitle

@@

%Unlike our method however, the iterations are composed of 
%Cubic-B-splines. The benefit of this method is that the result is a 
%differentiable path.

@@

%Let $\translation^{*}\in \real^3$ denotes the position between frames of $
%\body_1$  and $\body_2$ in configuration $\xx_i(\tcolli)$. Let $\translation \in 
%\real^3$ (resp. $R\in SO(3)$) denote the same position (resp. rotation) in 
%configuration $\xx (\tcolli)$ where $\xx$ is any path in $\CS^{wp}$.

%Let $M^{*}\in SE(3)$ denote the homogeneous transformation between frames of $
%\body_1$  and $\body_2$ in configuration 
%$\xx_i(\tcolli)$. Let $M\in SE(3)$ denote the same transformation in configuration 
%$\xx (\tcolli)$ where $\xx$ is any path 
%in $\CS^{wp}$. Let $R\in SO(3)$ and $\translation\in\real^3$ 
%(resp. $\translation^{*}$) be the rotation 
%and translation parts of $M$ (resp. $M^{*}$).

%We denote by $F$ the path constraint defined by the mapping from $\CS^{wp}$ to $
%\real^3$ defined by
%\begin{equation}\label{eq:constraint}
%F (\xx) =  \mathbf{u}^T R^T (\translation^{*} - \translation)
%\end{equation}
%where the product $R^T (\translation^{*} - \translation)$ is used to express the translations difference in the global frame ${\cal R}_0$.

\vspace{0.2cm}

%Therefore, the Jacobian $J_F$ of constraint~(\ref{eq:constraint}) with respect to 
%$x$ is
%$$
%J_F = \left(\begin{array}{cccccc}
%0 & \cdots & (1-\beta)\,\mathbf{u}^T \frac{\partial F}{\partial q} (\xx_j(t_{coll\,i})) & \
%\beta\,\mathbf{u}^T \frac{\partial F}{\partial q} (\xx_j(t_{coll\,i})) & \cdots & 0
%\end{array}
%\right)
%$$

\vspace{0.2cm}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=7.8cm]{contact_points6.png}
	\includegraphics[width=8cm]{contact_points2potential.png}
	\caption{Path-optimization results on 2D-ponctual robots, moving around 
	green obstacles. Initial paths are in red, optimized ones in black. Grey paths 
	represent intermediate iterations, red and black dots resp. $\po_1$ and $\po_2$ 
	points, red segments $\mathbf{u}$ and blue circles collision-free 
	configurations 
	of the backtracked paths 
	where constraints have been computed.}
	\label{2D_long}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=7.5cm]{local_box_optim.png}
	\caption{Case of a long initial path (above) containing a small part that can 
	be optimized (below). Random shortcut is unlikely to optimize the part 
	containing detours in the box, whereas our method 
	succeeds (in blue). This type of issue is common in navigation problems in 
	environments with long corridors.}
	\label{local_box_optim}
\end{figure}

@@

%\begin{figure}[b]
%	\centering
%	\includegraphics[width=5cm,height=3.5cm]{ur5_v2.png}
%	\caption{6-DOF robot arm on which our path-optimization has been tested.}
%	\label{ur5}
%\end{figure}

@@

%But we admit that restrincting the number of random shortcut iterations is 
%neither a acceptable criterion because of randomness.
%We also discuss the good properties and limits of our algorithm.

@@

% UR5-wall  OPTIONAL PART imo
%\begin{wrapfigure}[16]{r}{7cm}
%\centering
%\includegraphics[width=7cm]{ur5-wall-traj-rank-loss.png}
%\caption{UR5}
%\label{ur5-wall}
%\end{wrapfigure}
%In a much more cluttered environment Figure~\ref{ur5-wall} where the robot moves 
%throught a hole in a wall and between two cylinders, path reduction only manages to 
%reduce some but not 
%all detours. This behavior can be explained by a path over-constraining due to the 
%important proximity of the robot to the obstacles during the whole path, and 
%because there are not so many DOF to play on to easily avoid collisions and 
%return a small-cost solution.
%We advance this explanation because on the two following high-DOF examples of the 
%video (and Figure~\ref{pr2_final}) based on PR2, results are better 
%in terms of path length and quality.

@@

%The removal of the translation is also a consequence of our cost ponderation as described in the previous section.  NON ???

@@

Optimization computation time and path length averages are presented for 30 runs of 
each example in the Table~\ref{tab:results}.
It appears that our method presents 
similar computation times and path lengths for mobile manipulation tasks. However, 
the complete disappearance of the mobile base motion in the PRS and GB optimized 
paths is highlighted in the right column of Table~\ref{tab:results}. Thus the 
problem addressed Figure~\ref{decoupled_DOF_optimization} is solved considering this 
DOF.

@@

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{ccccc}
  \toprule
    \textbf{Problem} & Path obtained from & Computation time  & Path length & Base traveled distance\\
    \midrule
    \midrule
    & Initial &  & $21.9$  &\\
    \textbf{2D slidding-robot} & GB & $9.29\,\text{ms}$ & $17.0$  &\\
    \textbf{(Fig.~\ref{2D_long} right)} & PRS & $0.336\,\text{ms}$ & $21.7$  &\\
    & RS & $1.89\,\text{ms}$ & $6.05$  &\\
    \midrule
    & Initial &  & $ $  &\\
    \textbf{Freeflyer-} & GB & $\,\text{ms}$ & $ $  &\\
    \textbf{puzzle} & PRS & $\,\text{ms}$ & $ $  &\\
    & RS & $\,\text{ms}$ & $ $  &\\
    \midrule
    & Initial &  & $10.8$  &\\
    \textbf{Double-arm} & GB & $10.3\,\text{ms}$ & $4.79$  &\\
    \textbf{5-DOF} & PRS & $2.17\,\text{ms}$ & $8.08$  &\\
    & RS & $5.33\,\text{ms}$ & $6.24$  &\\
    \midrule
    & Initial &  & $12.6$  & $9.57$\,\text{m}\\
    \textbf{PR2-crossing-} & GB & $1.28\,\text{s}$ & $2.57$  & $0\,\text{m}$\\
    \textbf{arms} & PRS & $2.63\,\text{s}$ & $ 5.31$ & $0\,\text{m}$\\
    & RS & $1.92\,\text{s}$ & $3.59$ & $2.63\,\text{m}$\\
    \midrule
    & Initial &  & $15.3$ &\\
    \textbf{PR2-in-} & GB & $19.2\,\text{s}$ & $4.53$ &\\
    \textbf{kitchen-1} & PRS & $23.5\,\text{s}$ & $12.2$ &\\
    & RS & $9.88\,\text{s}$ & $5.75$ &\\
    \midrule
    & Initial &  & $ $ &\\
    \textbf{UR5-} & GB & $\,\text{s}$ & $ $ &\\
    \textbf{with-spheres} & PRS & $\,\text{s}$ & $ $ &\\
    & RS & $\,\text{s}$ & $ $ &\\
    \midrule
    & Initial &  & $ $ &\\
    \textbf{UR5-} & GB & $\,\text{s}$ & $ $ &\\
    \textbf{industrial-example} & PRS & $\,\text{s}$ & $  $ &\\
    & RS &  $\,\text{s}$ & $ $ &\\
    \midrule
    & Initial &  & $ $ &\\
    \textbf{Baxter-in-} & GB & $\,\text{s}$ & $ $ &\\
    \textbf{office} & PRS & $\,\text{s}$ & $ $ &\\
    & RS & $\,\text{s}$ & $ $ &\\
    \bottomrule
  \end{tabular}
  }%scalebox
\caption{Average results for 30 runs of several examples presented in the paper or 
the video. For each run, a solution path is planned by Visibility-PRM as initial 
guess for each optimizer.
For the PR2-crossing-arms example only, the right column represents the 
distance that is traveled by the robot mobile base during the different paths.
}
\label{tab:results}
\end{table}

@@

In a future work, we plan to study a combination of a random shortcut and the gradient-based optimizers since they seem to share a complementarity. .....

\bibliographystyle{tADR} % plain, alpha, abbr, unsrt
\bibliography{paper}

>>>>

% The following packages can be found on http:\\www.ctan.org
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{color}
\usepackage{graphicx} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{mathrsfs}
\DeclareMathOperator*{\argmin}{argmin}
\usepackage{algorithm}
\usepackage{algpseudocode}  %\usepackage[noend]{algpseudocode}
\algtext*{EndWhile}% Remove "end while" text
\algtext*{EndIf}% Remove "end if" text
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{proof}
\newtheorem{property}{Property}
\usepackage[numbers]{natbib}
\algnewcommand\algorithmicinput{\textbf{input:}}
\algnewcommand\INPUT{\item[\algorithmicinput]}
\algnewcommand\algorithmicoutput{\textbf{output:}}
\algnewcommand\OUTPUT{\item[\algorithmicoutput]}
\makeatletter
\makeatother
\usepackage{hyperref}

@@

\jvol{30} \jnum{15} \jyear{2016} \jmonth{August}

@@

\author{Myl\`{e}ne Campana$^{\ast}$ \thanks{$^\ast$Corresponding author. Email: mcampana@laas.fr}, Florent Lamiraux and Jean-Paul Laumond
\\\vspace{6pt}
{\em{LAAS-CNRS, 7 av. Colonel Roche, 31400 Toulouse, FRANCE}}
}
\maketitle

@@

@@

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=7.8cm]{contact_points6.pdf}
	\includegraphics[width=8cm]{contact_points2potential.pdf}
	\caption{Path-optimization results on 2D-ponctual robots, moving around 
	green obstacles. Initial paths are dashed and crosses represent contact points 
	related to collision-constraints.}
	\label{2D_long}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=7.5cm]{local_box_optim.png}
	\caption{Case of a long initial path in red (above) containing a small part 
	that can 
	be optimized (below). Random shortcut is unlikely to optimize the part 
	containing detours in the box, whereas our method 
	succeeds (in blue). This type of issue is common in navigation problems in 
	environments with long corridors.}
	\label{local_box_optim}
\end{figure}

@@

@@

@@

@@

@@

Optimization computation time and path length averages are presented for 30 runs of 
each example in the Table~\ref{tab:results}. In some cases $\alpha_{init}$ was reduced to comply with very narrow passages, or increased in the opposite case. 
It appears that, for non-high DOF examples, computation time is higher using the GB optimization. The worst case shows up for the puzzle problem where the number of constraints of GB is typically important.
On the other hand, our method almost always provides the shortest paths, whereas it is not even the best criterion to quantify the parasite motions disappearance.
Such results are the artefact of the termination conditions of RS and PRS, length reduction or affordable computation time. This is particularly visible for PRS which easily gives up in some problems, such as the 2D slidding-robot, the UR5-with-spheres or the puzzle.
Finally, the complete vanishing of the mobile base motion in the PRS and GB 
optimized paths is highlighted in the right column of Table~\ref{tab:results}. Thus 
the problem addressed Figure~\ref{decoupled_DOF_optimization} is solved considering 
this DOF.

@@

\begin{table}[ht]
\centering
\scalebox{0.9}{
  \begin{tabular}{ccccc}
  \toprule
    \textbf{Problem} & Path obtained from & Computation time  & Path length & Base traveled distance\\
    \midrule
    \midrule
    & Initial &  & $21.9$  &\\
    \textbf{2D slidding-robot} & GB & $9.29\,\text{ms}$ & $17.0$  &\\
    \textbf{(Fig.~\ref{2D_long} right)} & PRS & $0.336\,\text{ms}$ & $21.7$  &\\
    & RS & $1.89\,\text{ms}$ & $17.7$  &\\
    \midrule
    & Initial &  & $18.8$  &\\
    \textbf{Freeflyer-} & GB ($\alpha_{init}=0.05$) & $1.02\,\text{s}$ & $9.65$  &\\
    \textbf{puzzle} & PRS & $1.13\,\text{ms}$ & $18.8$  &\\
    & RS & $4.72\,\text{ms}$ & $10.3$  &\\
    \midrule
    & Initial &  & $10.8$  &\\
    \textbf{Double-arm} & GB & $10.3\,\text{ms}$ & $4.79$  &\\
    \textbf{5-DOF} & PRS & $2.17\,\text{ms}$ & $8.08$  &\\
    & RS & $5.33\,\text{ms}$ & $6.24$  &\\
    \midrule
    & Initial (RRT) &  & $4.97$ &\\
    \textbf{UR5-} & GB ($\alpha_{init}=0.4$) & $2.12\,\text{s}$ & $2.97$ &\\
    \textbf{with-spheres} & PRS & $0.884\,\text{s}$ & $4.56$ &\\
    & RS & $2.89\,\text{s}$ & $2.99$ &\\
    \midrule
    & Initial &  & $4.83$ &\\
    \textbf{UR5-} & GB ($\alpha_{init}=0.4$) & $314\,\text{ms}$ & $2.25$ &\\
    \textbf{industrial-example} & PRS & $30.2\,\text{ms}$ & $4.53$ &\\
    & RS &  $95.6\,\text{ms}$ & $2.16$ &\\
    \midrule
    & Initial &  & $20.2$ &\\
    \textbf{Baxter-in-} & GB & $22.7\,\text{s}$ & $6.65$ &\\
    \textbf{office} & PRS & $9.49\,\text{s}$ & $18.9$ &\\
    & RS & $3.13\,\text{s}$ & $11.9$ &\\
    \midrule
    & Initial &  & $12.6$  & $9.57$\,\text{m}\\
    \textbf{PR2-crossing-} & GB & $1.28\,\text{s}$ & $2.57$  & $0\,\text{m}$\\
    \textbf{arms} & PRS & $2.63\,\text{s}$ & $ 5.31$ & $0\,\text{m}$\\
    & RS & $1.92\,\text{s}$ & $3.59$ & $2.63\,\text{m}$\\
    \midrule
    & Initial &  & $15.3$ &\\
    \textbf{PR2-in-} & GB & $19.2\,\text{s}$ & $4.53$ &\\
    \textbf{kitchen-1} & PRS & $23.5\,\text{s}$ & $12.2$ &\\
    & RS & $9.88\,\text{s}$ & $5.75$ &\\
    \bottomrule
  \end{tabular}
  }%scalebox
\caption{Average results for 30 runs of several examples presented in the paper or 
the video. For each run, a solution path is planned by Visibility-PRM (unless `RRT' 
for RRT-connect is mentioned) as initial guess for each optimizer.
For the PR2-crossing-arms example only, the right column represents the 
distance that is traveled by the robot mobile base during the different paths.
}
\label{tab:results}
\end{table}

@@

In a future work, we plan to study .....

\section*{Funding}
This work has been supported by the project ERC Advanced Grant 340050 Actanthrope and by the FP~7 project Factory in a Day under grant agreement n°~609206.

\bibliographystyle{tADR}
\bibliography{paper}
